### 2009-01-31 articles/2009/geoinformatics/article.tex
More text
git-svn-id: https://svn.osgeo.org/qgis/trunk@10058 c8812cc2-4d05-0410-92ff-de0c093fc19c

The QGIS project is the work of a group of dedicated developers,
translators, documenters, release helpers, bug reporters, and promoters. Their 
contributions are mainly on a voluntary basis, except in a few cases where 
contributors are able to contribute to QGIS as part of their daily work. QGIS 
is managed by the Project Steering Committee (PSC), a five member committee
providing technical guidance, community liason, release management, and
financial/marketing activities. The work of the QGIS project process is
spread between numerous people who each have a specific area of
responsibility, and ad-hoc contributors.

These volunteers together with a large number of users make up the
world-wide QGIS comunity. Over time their efforts have resulted in a comprehensive,
valuable and useful code and documentation base which is free for everyone 
to use and improve upon.

@@

With community platforms such as our website, wiki, forums and blog the QGIS project
provides current news, release, usage, and development information. In most cases 
these community web sites permit user contributions after registering. 
The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable interface 
with other users and for discussions of QGIS in general. In the spirit of open 
process and sharing knowledge, contacting developers directly instead of going through 
these community based avenues of communication is frowned apon.

@@

QGIS has been designed with a plugin architecture and therefore new
customized features and functions can easily be added to the application.
Many of the features in QGIS are actually implemented as core or external
plugins.

@@

Beside these two respositories a number of QGIS developers provide and maintain
their own repositories. These can be added to the repository list of the
Python Plugin Installer.

@@

\subsubsection{Development of extensions as C++ or Python plugins}
There is a plugin interface that allows extensions to access the running QGIS
instance and to use and extend the objects in the core of QGIS. Plugins may be
written in C++ or in Python. The QGIS documentation contains simple examples
for both programming languages making it straightforward to start with plugin 
programming. The development of python plugins is especially fast and convenient. Simple plugins require only a few hours of development. As a result, an increasing number of users are contributing new plugins, of either specialized or general use.

@@

>>>>

The QGIS project is the work of a group of dedicated developers,
translators, documenters, release helpers, bug reporters, and promoters. Their 
contributions are mainly on a voluntary basis, except in a few cases where 
contributors are able to contribute to QGIS as part of their daily work. QGIS 
is managed by the Project Steering Committee (PSC), a five member committee
providing technical guidance, community liaison, release management, and
financial/marketing activities. The work of the QGIS project process is
spread between numerous people who each have a specific area of
responsibility, and ad-hoc contributors.

These volunteers together with a large number of users make up the
world-wide QGIS community. Over time their efforts have resulted in a comprehensive,
valuable and useful code and documentation base which is free for everyone 
to use and improve upon.

@@

With community platforms such as our website, wiki, forums and blog the QGIS project
provides current news, release, usage, and development information. In most cases 
these community web sites permit user contributions after registering. 
The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable interface 
with other users and for discussions of QGIS in general. In the spirit of open 
process and sharing knowledge, contacting developers directly instead of going through 
these community based avenues of communication is frowned upon.

@@

QGIS has been designed with a plugin architecture and therefore new
customised features and functions can easily be added to the application.
Many of the features in QGIS are actually implemented as core or external
plugins.

@@

Beside these two repositories a number of QGIS developers provide and maintain
their own repositories. These can be added to the repository list of the
Python Plugin Installer.

@@

\subsubsection{Development of extensions as C++ or Python plugins}
There is a plugin interface that allows extensions to access the running QGIS
instance and to use and extend the objects in the core of QGIS. Plugins may be
written in C++ or in Python. The QGIS documentation contains simple examples
for both programming languages making it straightforward to start with plugin 
programming. The development of python plugins is especially fast and convenient. Simple plugins require only a few hours of development. As a result, an increasing number of users are contributing new plugins, of either specialised or general use.

@@

\subsection{Who uses QGIS}
QGIS is now widely used by professionals, government and local agencies, universities and students, and amateurs alike, for a large variety of tasks, from simply viewing raster and vector data (especially useful is the capability to deal with PostGIS layers) to running complex and custom analyses through GRASS modules. Often is used to replace or integrate proprietary software, and several migrations have been accomplished or are underway, both in small and in large companies and public administrations. Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged intuitive.
